---
title: "Development Analysis *(WIP)*"
author: "Josiah Parry"
date: "April 25, 2016"
output: html_document
---

The purpose of this document is to compare the responses to the development portion of the Newfound Lake PPGIS Study. This analysis will explore the difference between Non-Member and Member responses. 

First I begin by creating two different data frames, one with members and the other with non-members.
```{r, include=FALSE}
library(dplyr)
library(cowplot)
library(ggplot2)
dev <- read.csv("/Users/Josiah/Google Drive/College/Spring 2016/PPGIS/Newfound_GIT/Data/clean_development.csv")
```

```{r}
member <- dev %>% filter(NLRA_Member == "Yes")
nonmmbr <- dev %>% filter(NLRA_Member == "No")
```
---
I first wanted to check to see if there were any significant differences in the genders of our respondents.

```{r}
p1 <- member %>% filter(Gender == "Male") %>% summarize(n = n())
p2 <-nonmmbr %>% filter(Gender == "Male") %>% summarize(n = n())

prop.test(x = c(p1$n, p2$n), n = c(dim(member)[1], dim(nonmmbr)[1]), correct = FALSE)
```

Responses by gender proportion significantly different `(p = 0.03)`. Members are 70% Male, 30% Female. Non-members are 45% male, 55% female. This is just good to note.

###Housing
Two sample t-tests were conducted to test for similarity in responses. 
```{r, results='hide'}
#High Density Apartments
t.test(member$highdensity_apartments, nonmmbr$highdensity_apartments)

#High Density Single Family Homes
t.test(member$highdensity_singlefamily, nonmmbr$highdensity_singlefamily)

#Rural Density > 10 Acres
t.test(member$ruraldensity_lessthan10, nonmmbr$ruraldensity_lessthan10)

#Rural Density < 10 Acres
t.test(member$ruraldensity_10plus, nonmmbr$ruraldensity_10plus)
 
#Workforce Housing
t.test(member$workforce_housing, nonmmbr$workforce_housing)

#Accessory Housing
t.test(member$accessory_apartments, nonmmbr$accessory_apartments)
```
###Non - housing developement 
Two sample t-tests were conducted to test for similarity in responses. 
```{r, results='hide'}
#Recreation
t.test(member$recreation, nonmmbr$recreation)
 
#Small Business
t.test(member$small_business, nonmmbr$small_business)
 
#Commercial Business
t.test(member$commercial_business, nonmmbr$commercial_business)
```
####Significant Differences (Members vs. Non-Members)

#####High Density Apartments
28.6% of members indicated an interest in developing high density apartments `(p=0.000)`. Whereas non-members did not once indicate an interest in developing apartments.

#####High Density Single Family Homes
43% of members indicated an interest in developing high density single family homes `(p=0.005)`. Only 12.5% of non-members indicated interest in developing high density single family homes.

####commercial business
31% of members indicated interest in developing commercial business, whereas only 8% of non-members indicated this interest `(p=0.017)`.

###Visualizing These Differences
```{r, echo = FALSE, fig.width=5, fig.height=8, fig.align='center'}
#Visualize Commercial Business
commercialviz <-  na.omit(dev) %>% 
  ggplot(aes(commercial_business)) + geom_bar(aes(y = (..count..)/sum(..count..)), fill = "#ffa24e") + 
  labs(title = "Commercial Business") + facet_wrap(~NLRA_Member) +
  scale_x_discrete(limits = c(0,1), labels = c("No", "Yes"))
#Adding Labels
commercialviz <- commercialviz + xlab("") + 
  ylab("Prop. of Total Respondents")

#Visualize High Density Single Family Homes
singlefamvis <- na.omit(dev) %>% 
  ggplot(aes(highdensity_singlefamily)) + geom_bar(aes(y = (..count..)/sum(..count..)), fill = "#ffa24e") + 
  labs(title = "High Density Single Family Homes") + facet_wrap(~NLRA_Member) +
  scale_x_discrete(limits = c(0,1), labels = c("No", "Yes")) + 
  labs(x = "", y = "Prop. of Total Respondents")

#Visualize differences in high density apartments
apartmentvis <- na.omit(dev) %>% 
  ggplot(aes(highdensity_apartments)) + geom_bar(aes(y = (..count..)/sum(..count..)), fill = "#ffa24e") + 
  labs(title = "High Density Apartments") + facet_wrap(~NLRA_Member) +
  scale_x_discrete(limits = c(0,1), labels = c("No", "Yes")) + 
  labs(x= "", y = "Prop. of Total Respondents")

plot_grid(apartmentvis, singlefamvis, commercialviz, nrow = 3)
```

