---
title: "Threats VS Conservation"
author: "Josiah Parry"
date: "Spring 2016"
output: html_document
---

One of the main questions we wanted to answer as a result of this study was: Do people want to conserve what they believe to be threatened? 

This will be an exploration of this question. I will compare the threat level ratings to the conservation priorities. The belief before beginning this analysis is that for variables listed in both conservation and threats, there should be *no* significant difference. 

```{r, include=F}
library(dplyr)
library(ggplot2)
```
First I must load the data:
```{r}
threats <- read.csv("/Users/Josiah/Google Drive/College/Spring 2016/PPGIS/Newfound_GIT/Data/clean_threats.csv")
conservation <- read.csv("/Users/Josiah/Google Drive/College/Spring 2016/PPGIS/Newfound_GIT/Data/clean_conservation.csv")
```

The first variable is a conservation priority, and the second is a percieved threat to the landscape. The comparisons are as follows:
 
 * Recreation & Recreation 
    + `p-value = 3.73e-05`
 * Viewshed & Scenic Quality 
    + `p-value < 2.2e-16`
 * Ecosystem & Soil Quality
    + `p-value < 2.2e-16`
 * Ecosystem & Water Quality
    + `p-value = 3.182e-09`
 * Ecosystem & Wildlife 
    + `p-value = 1.332e-11`
 * Economic & Business
    + `p-value = 1.011e-08`
 * Economic & Tourism
    + `p-value = 0.1073`
 * Culture & Rural Character
    + `p-value = 0.003662`


```{r, results='hide'}
#Recreation & Recreation
t.test(conservation$recreation, threats$recreation)

#Viewshed & Scenic Quality
t.test(conservation$viewshed, threats$scenic)

#Ecosystem & Soil 
t.test(conservation$ecosystem, threats$soil_quality)

#Ecosystem & Water
t.test(conservation$ecosystem, threats$waterquality)

#Ecosystem & Wildlife
t.test(conservation$ecosystem, threats$wildlife)

#Economic & Business 
t.test(conservation$economic, threats$business)

#Economic & Tourism
t.test(conservation$economic, threats$tourism)
  #NO SIG DIF

#Culture and Rural
t.test(conservation$culture, threats$rural)
```


Conservation is rated with a higher level of priority than their level of threat.Perhaps a "threat" is a much more abstract concept and is harder to tie to a landscape. Whereas the concept of conservation is much more visceral. 

This doesn't hold true for ratings of economic conservation and tourism. This can indicate New Hampshire's strong tie to tourism as a main driver of their economy. 